Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-04 PAPER.tex
compiled with 95% method 2 plot

Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis. As can be seen in Figure \ref{fig:Prob_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out. We can also see that, due to the small number of samples, the probability does not perfectly converge at high injected power levels. Rather than insist on a rejection at the $99$th percent level, we compromise at $90$\%.

The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text. Overall the limits are slightly lower, with k modes differing by factors of 3 to 37.

\begin{figure}[t]
\centering
\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
\caption{A comparison of the signal loss method described in Section \ref{sec:Sigloss}
with the method in this appendix at $90$\% confidence (red curve).
Also shown are the upper limits of the unweighted power spectrum
(blue dashed) and theoretical noise model (green). \label{fig:sigloss_compare} }
\end{figure}

>>>>

Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis. As can be seen in Figure \ref{fig:Prob_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out. We can also see that, due to the small number of samples, the probability does not perfectly converge at high injected power levels. Rather than insist on a rejection at the $99$th percent level, we compromise at $95$\%.

The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text. Overall the limits show good agreement, with k modes differing by factors of 2 to 4.

\begin{figure}[t]
\centering
\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison_95.png}
\caption{A comparison of the signal loss method described in Section \ref{sec:Sigloss}
with the method in this appendix at $95$\% confidence (red curve).
Also shown are the upper limits of the unweighted power spectrum
(blue dashed) and theoretical noise model (green).} 
\label{fig:sigloss_compare} 
\end{figure}
